Evaluation of the repository

### 2024-10-16 pages/repo_evaluation.qmd
docs(repo evaluation): add reflections and scatter plots for the first two summary charts, and N/N reproduced to all chart labels

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [3, 0, 9, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [5, 0, 7, 0],
  'Anagnostou et al. 2022': [10, 0, 2, 0],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [3, 0, 9, 0],
  'Wood et al. 2021': [4, 0, 8, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [0, 0, 12, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [3, 0, 9, 0],
  'Anagnostou et al. 2022': [5, 0, 7, 0],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [0, 0, 12, 0],
  'Wood et al. 2021': [5, 0, 7, 0]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and<br>Ramamohan 2021': [2, 0, 6, 0],
  'Huang et al. 2019': [2, 0, 6, 0],
  'Lim et al. 2020': [2, 0, 6, 0],
  'Kim et al. 2021': [4, 1, 3, 0],
  'Anagnostou et al. 2022': [7, 0, 1, 0],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [2, 0, 6, 0],
  'Wood et al. 2021': [2, 0, 6, 0]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and<br>Ramamohan 2021': [0, 0, 5, 0],
  'Huang et al. 2019': [2, 0, 3, 0],
  'Lim et al. 2020': [0, 0, 5, 0],
  'Kim et al. 2021': [0, 0, 5, 0],
  'Anagnostou et al. 2022': [1, 1, 3, 0],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [0, 0, 5, 0],
  'Wood et al. 2021': [0, 0, 5, 0]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T

>>>>

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [3, 0, 9, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [5, 0, 7, 0],
  'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
  'Wood et al. 2021 (5/5)': [4, 0, 8, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

::: {.callout icon=false collapse=true}

## Reflections

The studies meeting 33.3%, 41.7% and 83.3% of criteria were all fully reproduced.

The remaining four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.

However, I think it is more meaningful to actually look at what criteria were and were not met.

```{python}
import plotly.express as px

# Percentage of items reproduced, and percentage of badge criteria met
df = pd.DataFrame({
  'Shoaib and Ramamohan 2021': [94, 25],
  'Huang et al. 2019': [37.5, 25],
  'Lim et al. 2020': [100, 25],
  'Kim et al. 2021': [100, 41.7],
  'Anagnostou et al. 2022': [100, 83.3],
  #'Johnson et al. 2021': [],
  'Hernandez et al. 2015': [12.5, 25],
  'Wood et al. 2021': [100, 33.3]
}).T.reset_index()
df.columns = ['study', 'reproduce', 'criteria']

px.scatter(df, x='criteria', y='reproduce',
           hover_data={'study': True})
```

:::

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [0, 0, 12, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [3, 0, 9, 0],
  'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
  'Wood et al. 2021 (5/5)': [5, 0, 7, 0]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

::: {.callout icon=false collapse=true}

## Reflections

Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will quite weight what is met v.s. not.

Feel that looking at the criteria met is a bit more meaningful? And then specific examples of how that translates into badges - e.g. none meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.

```{python}
import plotly.express as px

# Percentage of items reproduced, and percentage of badges awarded
df = pd.DataFrame({
  'Shoaib and Ramamohan 2021': [94, 25],
  'Huang et al. 2019': [37.5, 0],
  'Lim et al. 2020': [100, 25],
  'Kim et al. 2021': [100, 25],
  'Anagnostou et al. 2022': [100, 41.7],
  #'Johnson et al. 2021': [],
  'Hernandez et al. 2015': [12.5, 0],
  'Wood et al. 2021': [100, 41.7]
}).T.reset_index()
df.columns = ['study', 'reproduce', 'badges']

px.scatter(df, x='badges', y='reproduce',
           hover_data={'study': True})
```

:::

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [2, 0, 6, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 6, 0],
  'Lim et al. 2020 (9/9)': [2, 0, 6, 0],
  'Kim et al. 2021 (10/10)': [4, 1, 3, 0],
  'Anagnostou et al. 2022 (1/1)': [7, 0, 1, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [2, 0, 6, 0],
  'Wood et al. 2021 (5/5)': [2, 0, 6, 0]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [0, 0, 5, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 3, 0],
  'Lim et al. 2020 (9/9)': [0, 0, 5, 0],
  'Kim et al. 2021 (10/10)': [0, 0, 5, 0],
  'Anagnostou et al. 2022 (1/1)': [1, 1, 3, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [0, 0, 5, 0],
  'Wood et al. 2021 (5/5)': [0, 0, 5, 0]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T
